---
title: "Data Description"

output: 
  html_document:
    toc: true
    toc_float: true
    
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Data Information

- The dataset used in this research is obtained from kaggle and updated in 2021.The dataset for our research project is a comprehensive collection of consumer behavior and demographic data encapsulating various aspects of online and in-store shopping habits, specifically focusing on grocery expenditures. It consists of 2240 observations, each representing an individual customer, and 29 variables capturing a wide range of information.

## Data Processing

- The dataset 2240 customer records, was imported into R using the `read_csv()` function. Superfluous columns such as `ID`, `Z_CostContact`, `Z_Revenue`, `NumCatalogPurchases`, and `NumDealsPurchases` were removed to hone in on variables pertinent to our analysis.

- During the cleaning phase, new variables were created: `Total_amount` to capture total spending, `Prefer_web_or_store` to indicate purchasing preference, `Accept_camps` to tally accepted marketing campaigns, and `Age` to reflect customer age at first purchase. The variable `NumWebVisitsMonth` was renamed to `WebVisits` for better interpretability.

- Following the removal of rows with missing values, the `Marital_Status` variable was streamlined by grouping uncommon statuses into an 'Other' category, simplifying the analysis. The final dataset is devoid of redundant information and is augmented with variables that provide a holistic view of customer behavior.


### The Final dataset contains the following 12 variables:

#### Demographics

- `Age`: Customer data minus date of birth
- `Education`: Customer's education level
- `Marital_Status`: Customer's marital status
- `Income`: Customer's yearly household income
- `Kidhome`: Number of children in customer's household
- `Teenhome`: Number of teenagers in customer's household
- `Recency`: Number of days since customer's last purchase
- `Complain`: 1 if the customer complained in the last 2 years, 0 otherwise


#### Consumptions

- `Total_amount`: Sum of the amount of products the customer purchased, included wines, fruits, meat, fish, sweet and gold.


#### Marketing Response

- `Accept_Camps`: if customer accepted the offer in the 1st campaign, 0 otherwise

#### Shopping Preference

- `Prefer_web_or_store`: Customer prefer web or in-store shopping
- `WebVisits`: Number of visits to company’s website in the last month




```{r message=FALSE}
# Load libraries
library(readr)
library(tidyverse)

# Read in data
data = read_csv("marketing_campaign.csv")

# Data manipulation
data = data %>%
  select(-ID, -Z_CostContact, -Z_Revenue, -NumCatalogPurchases, -NumDealsPurchases) %>%
  mutate(
    Total_amount = MntWines + MntFruits + MntMeatProducts + MntFishProducts + MntSweetProducts + MntGoldProds,
    Prefer_web_or_store = ifelse(NumStorePurchases > NumWebPurchases, "store", "web"),
    Accept_camps = AcceptedCmp1 + AcceptedCmp2 + AcceptedCmp3 + AcceptedCmp4 + AcceptedCmp5 + Response,
    Age = as.numeric(substr(Dt_Customer, 7, 10)) - Year_Birth
  ) %>%
  rename(WebVisits = NumWebVisitsMonth) %>%
  select(-MntWines, -MntFruits, -MntMeatProducts, -MntFishProducts, -MntSweetProducts, -MntGoldProds,-AcceptedCmp1, -AcceptedCmp2, -AcceptedCmp3, -AcceptedCmp4, -AcceptedCmp5, -Response, -Year_Birth, -Dt_Customer, -NumWebPurchases, -NumStorePurchases) %>%
  drop_na()

# Adjust Marital Status
data$Marital_Status[data$Marital_Status %in% c("Absurd", "Alone", "YOLO", "Widow")] = "Other"

```
