---
title: "Exploratory Data Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```


```{r}
library(readr)
library(tidyverse)

data <- read_csv("marketing_campaign.csv")

data <- data %>%  select(-ID, -Z_CostContact,  -Z_Revenue, -NumCatalogPurchases, -NumDealsPurchases)

data <- data %>%
  mutate(Total_amount = MntWines +  MntFruits +  MntMeatProducts +   MntFishProducts +
           MntSweetProducts +  MntGoldProds,
         Prefer_web_or_store = ifelse(NumStorePurchases > NumWebPurchases, "store", "web"),
         Accept_camps  =  AcceptedCmp1 +  AcceptedCmp2 +  AcceptedCmp3 +  AcceptedCmp4 +
           AcceptedCmp5 + Response,
         Age  = as.numeric(substr(Dt_Customer,7,10)) - Year_Birth,
         ) %>% rename("WebVisits" = "NumWebVisitsMonth")
  

data <- data %>% select(-MntWines, -MntFruits, -MntMeatProducts, 
                        -MntFishProducts, -MntSweetProducts, -MntGoldProds,
                        -AcceptedCmp1,-AcceptedCmp2,-AcceptedCmp3,
                        -AcceptedCmp4,-AcceptedCmp5 ,-Response,
                        -Year_Birth, -Dt_Customer,
                        -NumWebPurchases, -NumStorePurchases) %>% drop_na()

data$Marital_Status[data$Marital_Status %in% c("Absurd", "Alone","YOLO","Widow")] =  "Other"
   

```


# EDA

## Numerical summary 

Table 1 shows Data descriptive statistics grouped by prefer web or store for each variable

\newpage

```{r, results = "asis"}
library(gtsummary)
data  %>%
  tbl_summary(by = Prefer_web_or_store, type = list(Accept_camps ~ "continuous")) %>%
  add_p(pvalue_fun = ~ style_pvalue(.x, digits = 2)) %>%
  add_overall() %>%
  add_n() %>%
  modify_header(label ~ "**Variable**") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Prefer web or store**") %>%
  modify_footnote(
    all_stat_cols() ~ "Median (IQR) or Frequency (%)"
  ) %>%
  modify_caption("**Data descriptive statistics**") %>%
  bold_labels()
```

## Graphical summary 

* Figure 1 shows distributions of categorical covariates variables with prefer web or store

  The set of bar graphs present a comparative analysis of consumer preferences between in-store (depicted in purple) and web-based shopping (depicted in yellow) across various demographic segments and behavioral factors. 
  These segments and factors include: 
  Educational level, marital status, household composition, costumer feedback behavior, marketing campaign receptiveness

* Figure 2 shows distributions of response variable total amount with prefer web or store

  The image shows a box plot with two categories: 
  one for customers who prefer shopping in stores (red) and another for those who prefer shopping online (blue). 
  A box plot displays the range of spending, the median (middle value), and any outliers (unusually high or low values).

  In this plot, the median spending for in-store shoppers is lower, suggesting they generally spend less, but there are a few who spend a lot more, shown by the dots above the main box. 
  For online shoppers, the median spending is higher and more in the middle of the range, indicating a more balanced spending pattern, without any outliers. This suggests that people who shop online tend to spend more evenly, while those who shop in stores have a wider range of spending habits.

* Figure 3 shows distributions of continous covariates variables with prefer web or store

  The image shows four kernel density plots comparing the preferences for shopping in-store (shown in red) versus online (shown in blue) across different customer characteristics:
  Age, yearly income, web visits monthly, recency

```{r, fig.height=9.8, fig.width=9.8}
library(ggplot2)
library(ggthemes)
library(scales)
d <- data %>% group_by(Prefer_web_or_store,Education ) %>% count() %>%
  group_by(Education  ) %>% mutate(pct= n/sum(n))
g1 <- ggplot(d, aes(Education  , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Education level",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Marital_Status ) %>% count() %>%
  group_by(Marital_Status) %>% mutate(pct= n/sum(n))
g2 <- ggplot(d, aes(Marital_Status , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Marital status",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Kidhome ) %>% count() %>%
  group_by(Kidhome) %>% mutate(pct= n/sum(n))
g3 <- ggplot(d, aes(factor(Kidhome) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Number of small children",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Teenhome ) %>% count() %>%
  group_by(Teenhome) %>% mutate(pct= n/sum(n))
g4 <- ggplot(d, aes(factor(Teenhome) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Number of teenagers",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Complain ) %>% count() %>%
  group_by(Complain ) %>% mutate(pct= n/sum(n))
g5 <- ggplot(d, aes(factor(Complain ) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Complain or not",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Accept_camps ) %>% count() %>%
  group_by(Accept_camps ) %>% mutate(pct= n/sum(n))
g6 <- ggplot(d, aes(factor(Accept_camps ) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Accept number of campaigns",
       y = "Percentage",
       fill = "Prefer web or store")

library(cowplot)
plot_grid(g1,g2,g3,g4,g5,g6,nrow = 3)
```

\newpage
```{r, fig.height=4.8, fig.width=6.8}
g1 <- ggplot(data, aes(y=Total_amount)) +  geom_boxplot(aes( Prefer_web_or_store, fill = Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Total amount",
         fill="Prefer web or store") + theme_stata()
plotly::ggplotly( g1)
```

```{r, fig.height=6.8, fig.width=7.8}
g2 <- ggplot(data, aes(Income)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Yearly Income",
         fill="Prefer web or store")+ theme_economist()
g3 <- ggplot(data, aes(Recency)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Recency",
         fill="Prefer web or store")+theme_economist()
g4 <- ggplot(data, aes(WebVisits)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Web visits monthly",
         fill="Prefer web or store")+theme_economist()
g5 <- ggplot(data, aes(Age)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Age",
         fill="Prefer web or store")+theme_economist()
plot_grid(g5,g2,g4,g3,nrow = 2)
```
