---
title: "Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```



```{r}
library(readr)
library(tidyverse)

data <- read_csv("marketing_campaign.csv")

data <- data %>%  dplyr::select(-ID, -Z_CostContact,  -Z_Revenue, -NumCatalogPurchases, -NumDealsPurchases)

data <- data %>%
  mutate(Total_amount = MntWines +  MntFruits +  MntMeatProducts +   MntFishProducts +
           MntSweetProducts +  MntGoldProds,
         Prefer_web_or_store = ifelse(NumStorePurchases > NumWebPurchases, "store", "web"),
         Accept_camps  =  AcceptedCmp1 +  AcceptedCmp2 +  AcceptedCmp3 +  AcceptedCmp4 +
           AcceptedCmp5 + Response,
         Age  = as.numeric(substr(Dt_Customer,7,10)) - Year_Birth,
         ) %>% rename("WebVisits" = "NumWebVisitsMonth")
  

data <- data %>% select(-MntWines, -MntFruits, -MntMeatProducts, 
                        -MntFishProducts, -MntSweetProducts, -MntGoldProds,
                        -AcceptedCmp1,-AcceptedCmp2,-AcceptedCmp3,
                        -AcceptedCmp4,-AcceptedCmp5 ,-Response,
                        -Year_Birth, -Dt_Customer,
                        -NumWebPurchases, -NumStorePurchases) %>% drop_na()

data$Marital_Status[data$Marital_Status %in% c("Absurd", "Alone","YOLO","Widow")] =  "Other"
   

```


# Models

## Propensity score matching model

* useful for observational data

* balance is better after matching than before 

* after Propensity score matching model using linear regression model

```{r,results="asis"}
library(Matching)
# Estimate the propensity model
data2 <- data
data2$Prefer_web_or_store <- ifelse(data2$Prefer_web_or_store == "web",0,1)
#Propensity score matching
glm1  <- glm(Prefer_web_or_store ~ Education + Marital_Status+ Income+ Kidhome +Teenhome+ Recency +
               WebVisits + Complain +  Accept_camps  +   Age, family=binomial, data=data2)

library(gtsummary)

gtsummary::tbl_regression(glm1)

#stargazer::stargazer(glm1, header = FALSE, no.space = TRUE, title = "Propensity model")

X  <- glm1$fitted
Y  <- data2$Total_amount
Tr  <- data2$Prefer_web_or_store

# one-to-one matching with replacement (the "M=1" option)
rr  <- Match(Y=Y, Tr=Tr, X=X, M=1)

#covariate balance
#balance is better after matching than before 
#mb  <- MatchBalance(Prefer_web_or_store ~ Education + Marital_Status+ Income+ Kidhome +Teenhome+ Recency +
#               WebVisits + Complain +  Accept_camps  +   Age,data=data2 ,match.out=rr, nboots=10)

```


## Linear regression model

Hypotheses:

$$H_0: \mu_{store} \ge \mu_{web}~~ vs. ~~H_1: \mu_{store} <  \mu_{web}$$

Based on table 3, after controlling other important covariates, reject H0 due to p value < 0.05, so conclude there is significant edivence showing  customers who  prefer stores shopping customers would spend less compared with who prefer web shopping online.


```{r,results="asis"}
data3 <- data2[c(rr$index.treated, rr$index.control), ]

model <- lm(Total_amount ~ ., data = data3)

gtsummary::tbl_regression(model )

#stargazer::stargazer(model, header = FALSE, type = "html", no.space = TRUE, title = "Regression summary")

```








