---
title: "Project Report"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

# Data cleaning

* Add amount of wines, fruits, meat ... into total amount spend

* Create a prefer web or store option: number of web > store, prefer "web", vice versa

* add total of accepted compaigns

* Age: be customer date minus year birth

* Marital_Status in  ("Absurd", "Alone","YOLO","Widow") merged into "Other"

* Remove missing values in Income

* final data has variables  "Education"  "Marital_Status"  "Income"   "Kidhome" "Teenhome"  "Recency"  "WebVisits"   "Complain"      "Total_amount"   "Prefer_web_or_store" "Accept_camps"  "Age", other variables omitted

* final data has 2216 obs with 12 variables

```{r}
library(readr)
library(tidyverse)

data <- read_csv("marketing_campaign.csv")

data <- data %>%  select(-ID, -Z_CostContact,  -Z_Revenue, -NumCatalogPurchases, -NumDealsPurchases)

data <- data %>%
  mutate(Total_amount = MntWines +  MntFruits +  MntMeatProducts +   MntFishProducts +
           MntSweetProducts +  MntGoldProds,
         Prefer_web_or_store = ifelse(NumStorePurchases > NumWebPurchases, "store", "web"),
         Accept_camps  =  AcceptedCmp1 +  AcceptedCmp2 +  AcceptedCmp3 +  AcceptedCmp4 +
           AcceptedCmp5 + Response,
         Age  = as.numeric(substr(Dt_Customer,7,10)) - Year_Birth,
         ) %>% rename("WebVisits" = "NumWebVisitsMonth")
  

data <- data %>% select(-MntWines, -MntFruits, -MntMeatProducts, 
                        -MntFishProducts, -MntSweetProducts, -MntGoldProds,
                        -AcceptedCmp1,-AcceptedCmp2,-AcceptedCmp3,
                        -AcceptedCmp4,-AcceptedCmp5 ,-Response,
                        -Year_Birth, -Dt_Customer,
                        -NumWebPurchases, -NumStorePurchases) %>% drop_na()

data$Marital_Status[data$Marital_Status %in% c("Absurd", "Alone","YOLO","Widow")] =  "Other"
   

```


# EDA

## Numerical summary 

Table 1 shows Data descriptive statistics grouped by prefer web or store for each variable

\newpage

```{r, results = "asis"}
library(gtsummary)
data  %>%
  tbl_summary(by = Prefer_web_or_store, type = list(Accept_camps ~ "continuous")) %>%
  add_p(pvalue_fun = ~ style_pvalue(.x, digits = 2)) %>%
  add_overall() %>%
  add_n() %>%
  modify_header(label ~ "**Variable**") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Prefer web or store**") %>%
  modify_footnote(
    all_stat_cols() ~ "Median (IQR) or Frequency (%)"
  ) %>%
  modify_caption("**Data descriptive statistics**") %>%
  bold_labels()
```

## Graphical summary 

* Figure 1 shows distributions of categorical covariates variables with prefer web or store

* Figure 2 shows distributions of response variable total amount with prefer web or store

* Figure 3 shows distributions of continous covariates variables with prefer web or store


```{r, fig.height=9.8, fig.width=9.8}
library(ggplot2)
library(ggthemes)
library(scales)
d <- data %>% group_by(Prefer_web_or_store,Education ) %>% count() %>%
  group_by(Education  ) %>% mutate(pct= n/sum(n))
g1 <- ggplot(d, aes(Education  , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Education level",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Marital_Status ) %>% count() %>%
  group_by(Marital_Status) %>% mutate(pct= n/sum(n))
g2 <- ggplot(d, aes(Marital_Status , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Marital status",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Kidhome ) %>% count() %>%
  group_by(Kidhome) %>% mutate(pct= n/sum(n))
g3 <- ggplot(d, aes(factor(Kidhome) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Number of small children",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Teenhome ) %>% count() %>%
  group_by(Teenhome) %>% mutate(pct= n/sum(n))
g4 <- ggplot(d, aes(factor(Teenhome) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Number of teenagers",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Complain ) %>% count() %>%
  group_by(Complain ) %>% mutate(pct= n/sum(n))
g5 <- ggplot(d, aes(factor(Complain ) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Complain or not",
       y = "Percentage",
       fill = "Prefer web or store")

d <- data %>% group_by(Prefer_web_or_store,Accept_camps ) %>% count() %>%
  group_by(Accept_camps ) %>% mutate(pct= n/sum(n))
g6 <- ggplot(d, aes(factor(Accept_camps ) , pct, fill =  Prefer_web_or_store)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_viridis_d() +
  theme_economist_white() +
  labs(x = "Accept number of campaigns",
       y = "Percentage",
       fill = "Prefer web or store")

library(cowplot)
plot_grid(g1,g2,g3,g4,g5,g6,nrow = 3)
```

\newpage
```{r, fig.height=4.8, fig.width=6.8}
g1 <- ggplot(data, aes(y=Total_amount)) +  geom_boxplot(aes( Prefer_web_or_store, fill = Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Total amount",
         fill="Prefer web or store") + theme_stata()
plotly::ggplotly( g1)
```

```{r, fig.height=6.8, fig.width=7.8}
g2 <- ggplot(data, aes(Income)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Yearly Income",
         fill="Prefer web or store")+ theme_economist()
g3 <- ggplot(data, aes(Recency)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Recency",
         fill="Prefer web or store")+theme_economist()
g4 <- ggplot(data, aes(WebVisits)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Web visits monthly",
         fill="Prefer web or store")+theme_economist()
g5 <- ggplot(data, aes(Age)) +  geom_density(aes(fill= Prefer_web_or_store), alpha=0.8) + 
    labs(title="", 
         x="Age",
         fill="Prefer web or store")+theme_economist()
plot_grid(g5,g2,g4,g3,nrow = 2)
```

# Models

## Propensity score matching model

* useful for observational data

* balance is better after matching than before 

* after Propensity score matching model using linear regression model

```{r,results="asis"}
library(Matching)
# Estimate the propensity model
data2 <- data
data2$Prefer_web_or_store <- ifelse(data2$Prefer_web_or_store == "web",0,1)
#Propensity score matching
glm1  <- glm(Prefer_web_or_store ~ Education + Marital_Status+ Income+ Kidhome +Teenhome+ Recency +
               WebVisits + Complain +  Accept_camps  +   Age, family=binomial, data=data2)

library(gtsummary)

gtsummary::tbl_regression(glm1)

#stargazer::stargazer(glm1, header = FALSE, no.space = TRUE, title = "Propensity model")

X  <- glm1$fitted
Y  <- data2$Total_amount
Tr  <- data2$Prefer_web_or_store

# one-to-one matching with replacement (the "M=1" option)
rr  <- Match(Y=Y, Tr=Tr, X=X, M=1)

#covariate balance
#balance is better after matching than before 
#mb  <- MatchBalance(Prefer_web_or_store ~ Education + Marital_Status+ Income+ Kidhome +Teenhome+ Recency +
#               WebVisits + Complain +  Accept_camps  +   Age,data=data2 ,match.out=rr, nboots=10)

```


## Linear regression model

Hypotheses:

$$H_0: \mu_{store} \ge \mu_{web}~~ vs. ~~H_1: \mu_{store} <  \mu_{web}$$

Based on table 3, after controlling other important covariates, reject H0 due to p value < 0.05, so conclude there is significant edivence showing  customers who  prefer stores shopping customers would spend less compared with who prefer web shopping online.


```{r,results="asis"}
data3 <- data2[c(rr$index.treated, rr$index.control), ]

model <- lm(Total_amount ~ ., data = data3)

gtsummary::tbl_regression(model )

#stargazer::stargazer(model, header = FALSE, type = "html", no.space = TRUE, title = "Regression summary")

```








